R Notebook

### 2018-03-16 paper/docs/04_Modelresults_50.Rmd
add crosscorrelation

theme_set(
  theme_bw(base_family = "Roboto", base_size = 10) +
    theme(
      plot.title = element_text(size = 14,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 8),
      plot.caption = element_text(size = 6),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      panel.background  = element_rect("#fafafa"),
      panel.border = element_blank()
    )
)

@@

```{r caching, echo = FALSE}
load("../output/btw_out2.Rda")
```

@@

$$
\theta_d=\alpha+\beta_1x_{ownership}+\beta_2x_{month}+\epsilon
$$

@@

@@

## Monthly
polls_monthly <- polls %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val) %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  transmute(Union = normalize_data(Union),
         SPD = normalize_data(SPD),
         Grüne = normalize_data(Grüne),
         FDP = normalize_data(FDP),
         AfD = normalize_data(AfD),
         yearmonth = yearmonth)

polls_monthly %>%
  gather(key = party, value = poll, Union:AfD) %>%
  ggplot(aes(yearmonth, poll, color = party)) +
  geom_line() +
  scale_color_manual(values = c("skyblue", "gold", "limegreen", "red", "black")) +
  labs(x="", y="", title = "Survey Value", 
       subtitle = "weekly", color = "") +
  geom_vline(xintercept = as.Date("2017-09-24"), 
             linetype = 2, color = col[3]) +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET"))
```

```{r fig.height=12, fig.width=10}
### by time
group1 <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### by time and site
group2 <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))
```

#### 3.1. Cross-Correlation
```{r}
group1 %>%
  select(yearmonth, topic_name, sentiment_n) %>%
  spread(topic_name, sentiment_n)  -> corr1

@@

corr <- expand.grid(names(corr1), names(corr2))
corr$correlation <- NA
```

```{r}
x <- 1

for (corr1Id in 1:ncol(corr2)) {
  c1 = corr2[,corr1Id]
  #print(names(corr2[,corr1Id]))
  for(corr2Id in 1:ncol(corr1)) {
    c2 = corr1[,corr2Id]
    #print(names(corr1[,corr2Id]))
    correlation = ccf(c1, c2, lag.max = 0,
                      na.action = na.contiguous, plot=F)
    corr[x,3] <- correlation$acf[1]

    x<- x+1
  }
}
```

```{r}
ggplot(corr, aes(Var2, Var1,
                 fill = correlation,
                 label = round(correlation,2))) +
  geom_tile(color="white") +
  geom_text(size = 3, color = col[5]) +
  viridis::scale_fill_viridis() +
  labs(x="", y="", title = "Cross Correlation of Polls vs. Sentiment Value")
```

@@

##### 3.2.1. CDU
```{r fig.height=10, fig.width=12}
### Plot 1  
plot1 <- group1 %>%
  filter(grepl(paste("CDU","CSU",sep="|"), topic_name))

p1 <- ggplot() +
  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
    geom_line(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +
  # Add poll line
  geom_line(data = polls_monthly, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### Plot 2
plot2 <- group2 %>%
  filter(grepl(paste("CDU","CSU",sep="|"), topic_name))

p2 <- ggplot() +
  geom_col(data = plot2,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
    scale_fill_manual(values = col) +
    scale_color_manual(values = col) +
  geom_line(data = plot2,
            aes(yearmonth, sentiment_n,
                group = topic_name,
                color = topic_name),
            show.legend = F) +
  facet_wrap(~site, ncol = 2) +
   # Add poll line
  geom_line(data = polls_monthly, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
```

#### SPD
```{r fig.height=12, fig.width=10}
plot1 <- group1 %>%
  filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +
   geom_line(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
  # Add poll line
  geom_line(data = polls_monthly, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
plot2 <- group2 %>%
  filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))

### Plot 2
p2 <- ggplot() +
  geom_col(data = plot2,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +
     geom_line(data=plot2, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
   # Add poll line
  geom_line(data = polls_monthly, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))
```

>>>>

theme_set(
  theme_bw(base_family = "Roboto", base_size = 10) +
    theme(
      plot.title = element_text(size = 14,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 8),
      plot.caption = element_text(size = 6),
      panel.border = element_blank()
    )
)

@@

```{r caching, echo = FALSE}
load("../output/btw_out2.Rda")

btw <- btw %>%
  mutate(site = ifelse(site == "welt.de", "DIE WELT", site),
         site = ifelse(site == "zeit.de", "ZEIT ONLINE", site),
         site = ifelse(site == "focus.de", "FOCUS ONLINE", site),
         site = ifelse(site == "spiegel.de", "SPIEGEL ONLINE", site),
         site = ifelse(site == "tagesschau.de", "Tagesschau.de", site))
```

@@

$$
\theta_d=\alpha+\beta x_{ownership}+\epsilon
$$

@@

![Estimates](../figs/estimates.png)

@@

## Monthly
# polls_monthly <- polls %>%
#   group_by(yearmonth,party) %>%
#   summarise(mean_val = mean(value, na.rm=T)) %>%
#   ungroup() %>%
#   filter(!party %in% c("Piraten", "Sonstige")) %>%
#   filter(mean_val != "NaN") %>%
#   mutate(mean_val = normalize_data(mean_val)) %>%
#   select(party, yearmonth, mean_val) %>%
#   spread(party, mean_val) %>%
#   filter(yearmonth > as.Date("2017-05-01"))

polls_monthly <- polls %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(!party %in% c("Piraten", "Sonstige")) %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val) %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  filter(yearmonth < as.Date("2018-03-01")) %>%
  mutate(AfD = normalize_data(AfD),
         FDP = normalize_data(FDP),
         Grüne = normalize_data(Grüne),
         Linke = normalize_data(Linke),
         SPD = normalize_data(SPD),
         Union = normalize_data(Union))

polls_monthly %>%
  gather(key = party, value = poll, AfD:Union) %>%
  ggplot(aes(yearmonth, poll, color = party)) +
  geom_line() +
  scale_color_manual(values =  c("deepskyblue", "gold", "limegreen", "deeppink", "red", "black")) +
  labs(x="", y="", title = "Survey Value", 
       subtitle = "weekly", color = "") +
  geom_vline(xintercept = as.Date("2017-09-24"), 
             linetype = 2, color = col[3]) +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%b", tz="CET")) +
    theme(axis.text.x = element_text(size = 10))
```

Normalize topic-sentiment value

A)
```{r fig.height=12, fig.width=10}
### by time
# group1 <- sentDF.values %>%
#   group_by(yearmonth, topic_name, topic) %>%
#   summarise(sentiment = mean(sentiment, na.rm=T),
#             obs = n()) %>%
#   ungroup() %>%
#   left_join(., tally_month, by="yearmonth") %>%
#   mutate(w = obs / total_obs,
#          sentiment_w = sentiment * w,
#          sentiment_n = normalize_data(sentiment_w))

### by time and site
# group2 <- sentDF.values %>%
#   group_by(yearmonth, topic_name, topic, site) %>%
#   summarise(sentiment = mean(sentiment, na.rm=T),
#             obs = n()) %>%
#   ungroup() %>%
#   left_join(., tally_month_site, by=c("yearmonth","site")) %>%
#   mutate(w = obs / total_obs,
#          sentiment_w = sentiment * w,
#          sentiment_n = normalize_data(sentiment_w))
```

B)
```{r}
### by time
group1 <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w)

group1 <- group1 %>%
  select(yearmonth, topic, sentiment_w) %>%
  spread(topic, sentiment_w) %>%
  lapply(normalize_data) %>%
  as.data.frame() %>%
  gather(topic, sentiment_n, -yearmonth) %>%
  mutate(topic = as.numeric(gsub("X","", topic))) %>%
  merge(., group1, by = c("topic", "yearmonth"))

### by time and site
group2 <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w)

group2 <- group2 %>%
  select(yearmonth, topic, site, sentiment_w) %>%
  spread(topic, sentiment_w) %>%
  lapply(normalize_data) %>%
  as.data.frame() %>%
  gather(topic, sentiment_n, -yearmonth, -site) %>%
  mutate(topic = as.numeric(gsub("X","", topic))) %>%
  merge(., group2, by = c("topic", "yearmonth","site"))
```

#### 3.1. Cross-Correlation

```{r}
plot_ccf <- function(corr1, corr2, ...){

  # Create empty matrix
  corr <- expand.grid(names(corr1), names(corr2))
  corr$correlation <- NA

  x <- 1

  for (corr1Id in 1:ncol(corr2)) {
    c1 = corr2[,corr1Id]
    #print(names(corr2[,corr1Id]))

    for(corr2Id in 1:ncol(corr1)) {
      c2 = corr1[,corr2Id]
      #print(names(corr1[,corr2Id]))
      correlation = ccf(c1, c2, lag.max = 0,
                      na.action = na.contiguous, plot=F)
      corr[x,3] <- correlation$acf[1]

      x<- x+1
    }
  }

      ### Plot Corr ##
      ggplot(corr, aes(Var2, Var1,
                 fill = correlation,
                 label = round(correlation,2))) +
        geom_tile(color="white", ...) +
        geom_text(size = 3.5, color = col[5]) +
        viridis::scale_fill_viridis(limits=c(-1, 1)) +
        labs(x="", y="", fill="",
             title = "Cross-Correlation / Polls vs. Sentiment Value",
             ...)
}
```

##### 3.1.1. Overall
```{r fig.height=6, fig.width=8}
group1 %>%
  select(yearmonth, topic_name, sentiment_n) %>%
  spread(topic_name, sentiment_n) %>%
  select(- yearmonth) -> corr1

@@

plot_ccf(corr1, corr2)
```

##### 3.1.2. By Media
```{r eval=FALSE, include=FALSE}
for (i in unique(group2$site)) {

  group2 %>%
  filter(site == i) %>%
  select(yearmonth, topic_name, sentiment_n) %>%
  spread(topic_name, sentiment_n) %>%
  select(- yearmonth) -> corr1

  p <- plot_ccf(corr1, corr2,
                show.legend = F,
                subtitle = paste(i)
                )

  ggsave(filename = paste0("../figs/corrplot_",i,".png"),
         height = 5)
}

<img src="../figs/corrplot_Bild.de.png", width = "49%">
<img src="../figs/corrplot_DIE WELT.png", width = "49%">
<img src="../figs/corrplot_FOCUS ONLINE.png", width = "49%">
<img src="../figs/corrplot_SPIEGEL ONLINE.png", width = "49%">
<img src="../figs/corrplot_stern.de.png", width = "49%">
<img src="../figs/corrplot_Tagesschau.de.png", width = "49%">
<img src="../figs/corrplot_ZEIT ONLINE.png", width = "49%">

@@

```{r}
plot_Poll_Sent <- function(filters, party_str, color_str) {

  ### Plot 1  
  plot1 <- group1 %>%
    filter(grepl(filters, topic_name))

  p1 <- ggplot() +
    geom_col(data=plot1, aes(yearmonth, sentiment_n,
                             group = topic_name,
                             fill = topic_name),
             position = "dodge",
             alpha = 0.5) +
    scale_fill_manual(values = col) +

    geom_line(data=plot1, aes(yearmonth, 
                              sentiment_n,
                              group = topic_name,
                              color = topic_name),
              show.legend = F) +
    scale_color_manual(values = col) +
    guides(fill = guide_legend(ncol=3)) +

    # Add poll line
    geom_line(data = polls_monthly,
              aes_string("yearmonth", party_str),
              color = color_str,
                            size = 0.9,
              linetype = 2) +
    labs(y="", x="", fill="",
         title = "Sentiment & Poll Values",
         subtitle = party_str,
         caption = "Both scores are normalized") +
    scale_x_date(breaks = date_breaks("1 month"), 
                 labels=date_format("%B", tz="CET")) +
    theme(legend.position = "bottom")

  ### Plot 2
  plot2 <- group2 %>%
    filter(grepl(filters, topic_name))

  p2 <- ggplot() +
    geom_col(data = plot2,
             aes(yearmonth, sentiment_n, 
                 group = topic_name,
                 fill = topic_name),
             alpha = 0.5,
             position = "dodge") +
    scale_fill_manual(values = col) +
    scale_color_manual(values = col) +

    geom_line(data = plot2,
              aes(yearmonth, sentiment_n,
                  group = topic_name,
                  color = topic_name),
              show.legend = F) +
    facet_wrap(~site, ncol = 2) +

    # Add poll line
    geom_line(data = polls_monthly, 
              aes_string("yearmonth", party_str),
              color = color_str,
              size = 0.9,
              linetype = 2) +
    labs(y="", x="", fill="") +
    scale_x_date(breaks = date_breaks("1 month"), 
                 labels=date_format("%B", tz="CET")) +
    theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

  p1 + p2 + plot_layout(ncol = 1, heights = c(1,4))

##### 3.2.1. CDU
```{r fig.height=12, fig.width=10}
filters <- paste("CDU","CSU","Great Coalition", sep="|")

### Plot 1  
plot_Poll_Sent(filters, "Union", "black")
```

#### SPD
```{r fig.height=12, fig.width=10}
filters <- paste("SPD","Great Coalition", sep="|")

plot_Poll_Sent(filters, "SPD", "black")
```

##### 3.2.3. AfD
```{r fig.height=12, fig.width=10}
filters <- paste("AfD", sep="|")

plot_Poll_Sent(filters, "AfD", "black")
```

#### FDP
```{r fig.height=12, fig.width=10}
filters <- paste("Jamaica", sep="|")

plot_Poll_Sent(filters, "FDP", "black")
```

#### Grüne
```{r fig.height=12, fig.width=10}
filters <- paste("Grüne","Jamaica", sep="|")

plot_Poll_Sent(filters, "Grüne", "black")
```

### 2018-03-16 paper/writing/structure.tex
add crosscorrelation

Some conclusions can be drawn from this illustration. First of all, it can be seen that, on average, all topics are discussed almost exclusively negatively. An exception is topic 27 concerning the Jaimaica coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017). In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly.

Concerning the issues that discuss the great coalition between CDU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises. However, the sentiment score of topics that deal with the SPD alone (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline. The topic, which contains the CDU in isolation (46), is rather zigzagging, with a low peak in October 2017.

>>>>

Some conclusions can be drawn from this illustration. First of all, it can be seen that, on average, all topics are discussed almost exclusively negatively. An exception is topic 27 concerning the Jamaica coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017). In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly, but then rises again in February. Concerning the issues that discuss the great coalition between CDU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises. However, the sentiment score of topics that deal with the SPD (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline. For the other parties the process is rather zigzag-like.
